Modular properties of string, branching and dual functions

### 2010-08-01 AffineLieAlgebras/DualFunctions/ModularProperties.tex
Mod prop

>>>>

For $N\in \mathbb{N},$ define
\begin{equation}
  \label{eq:12}
  \Gamma(N)=\left\{
      \begin{pmatrix} a & b \\ c & d
      \end{pmatrix}
      \right|\left.
        \begin{matrix}
          a,b,c,d\in \mathbb{Z},\quad ad-bc=1\\
          a\equiv d\equiv 1\; \text{mod}\; N,\quad b\equiv c\equiv 0\; \text{mod}\; N
        \end{matrix}
      \right\}
  \end{equation}
The subgroup $\Gamma(N)$ has {\it finite index} (define!) in $\Gamma(1)=SL(2,\mathbb{Z})$. For any $\tau\in \mathbb{C}$ there exists element of $SL(2,\mathbb{Z})$, which transforms it to the fundamental domain.

For $A\in SL(2,\mathbb{Z})$ define
\begin{equation}
  \label{eq:13}
  j(A,\tau)=c\tau+d.
\end{equation}
Note that
\begin{equation}
  \label{eq:14}
  j(BA,\tau)=j(B,A\tau)j(A,\tau).
\end{equation}
For any subgroup $\Gamma$ of finite index define a {\bf multiplier system} $\chi$ as a mapping
\begin{equation}
  \label{eq:15}
  \chi:\Gamma\to U(1).
\end{equation}
Let $k\in \mathbb{R}$. A complex valued holomorphic function $f$ on the upper half-plane of the complex plane is a modular form of weight $k$ with respect to $\Gamma$ if there exists a multiplier system $\chi$ for $\Gamma$ with
\begin{equation}
  \label{eq:16}
  f(\tau)=\chi(A) j(A,\tau)^{-k} f(A\tau),
\end{equation}
for all $\tau$ in the upper half-plane and $A\in \Gamma$.
